%-------------------------
% Resume in Latex
% Author : Bryan Aneyro
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Bryan Aneyro Hernandez} \\ \vspace{1pt}
    Houston, Texas, 77038 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 954-297-1787 ~ \href{mailto:brah0211@outlook.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{Email}} ~ 
    \href{https://linkedin.com/in/bryananeyro}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/Asere231}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
    \href{https://www.bitbybryan.com}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{-8pt}
\end{center}

%-----------Summary-----------
\section{Summary}
\small{
Recent Computer Science graduate with a strong foundation in algorithms, data structures, and backend development. Skilled in building scalable web services, REST APIs, and full-stack applications using Java, Python, Node.js, and MongoDB. Proven ability to work in Agile teams, solve complex problems, and deliver production-grade software.\\
\textbf{Actively seeking Software Engineer or Backend Developer roles to contribute to innovative, mission-driven teams.}
}

    

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Aug. 2021 -- May 2025}
      {Bachelor of Science in Computer Science}{Overall Cumulative GPA, 3.476}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Data Structures
                \item Algorithms Analysis
                \item Senior Design I and II
                \item Processes for Object-Oriented Software Development
                \item OOP Java (\underline{\href{https://github.com/Asere231/Java_OOP}{here}})
                \item Robot Vision (\underline{\href{https://github.com/Asere231/Robot-Vision}{here}})
                \item Enterprise Computing (\underline{\href{https://github.com/Asere231/Enterprise-Computing}{here}})
                \item System Software (\underline{\href{https://github.com/Asere231/PL-0-Compiler}{here}})
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{PL/0 Compiler } $|$ \emph{ C, Compiler Design } $|$ \emph{ Repository: PL-0-Compiler}}{}
              \resumeItemListStart
                \resumeItem{Collaborated on building a four-module compiler for the PL/0 language targeting a virtual machine.}
                \resumeItem{Designed and implemented lexical analysis, parsing, and code generation from scratch using C.}
                \resumeItem{Gained deep understanding of symbol tables, grammar parsing, and runtime environments.}
              \resumeItemListEnd  
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{GroupFinder } $|$ \emph{ MERN Stack, Flutter } $|$ \emph{ Repository: GroupFinder}}{}
          \resumeItemListStart
            \resumeItem{Contributed to the development of a web and mobile app to help students find and join real-time study groups in the university library.}
            \resumeItem{Developed full-stack study group platform for students to coordinate in real-time using Flutter and MERN stack.}
            \resumeItem{Designed RESTful backend in Node.js/Express, integrated MongoDB with Mongoose, and implemented JWT-based auth.}
            \resumeItem{Enabled interactive map-based UI to join/create study groups with socket updates; deployed on Android and Web.}
          \resumeItemListEnd
          \vspace{-13pt}
            \resumeProjectHeading
        {\textbf{Bit by Bryan (Personal Portfolio Website) } $|$ \emph{ Next.js, Tailwind CSS, React, GSAP } $|$ \emph{ Repository: my-portfolio}}{}
          \resumeItemListStart
            \resumeItem{Created a personal portfolio with Next.js and Tailwind CSS to highlight projects and resume; deployed via Vercel.}
            \resumeItem{Enhanced UX with GSAP and Framer Motion animations and mobile responsiveness.}
            \resumeItem{Implemented custom carousel for project display and stylized navigation with GooeyNav and BlurText components.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
              {\textbf{Neural Networks and CNN Training } $|$ \emph{ Python, PyTorch, Jupyter Notebook } $|$ \emph{ Repository: Robot-Vision(project2)}}{}
              \resumeItemListStart
                \resumeItem{Built and trained deep learning models using PyTorch for image classification tasks on MNIST and CIFAR-10 datasets.}
                \resumeItem{Built and tested shallow and deep neural nets with various architectures and activations.}
                \resumeItem{Trained CNNs with varied filter sizes and settings; compared learning rates and epochs.}
                \resumeItem{Visualized loss and accuracy metrics during training to analyze model behavior and effectiveness.}
              \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{RE-RASSOR: New Arm (Senior Design) } $|$ \emph{ ROS2, Gazebo, MoveIt2, Python, Ubuntu } $|$ \emph{ Repository: FSI-CS-Arm}}{}
          \resumeItemListStart
            \resumeItem{Contributed to the development of a robotic arm with 4 joints for a lunar rover in a year-long senior design project.}
            \resumeItem{Helped simulate and control robotic motion using Gazebo and MoveIt2, integrating URDF/Xacro robot descriptions.}
            \resumeItem{Implemented ROS2 nodes in Python and C++ to manage inverse kinematics, joint actuation, and trajectory planning.}
            \resumeItem{Worked collaboratively within a multidisciplinary team to integrate the arm into a full robotic rover system and validate performance in simulation.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Java, Python, C, JavaScript, HTML, CSS} \\
    \textbf{Frameworks / Libraries}{: Node.js, Express.js, React.js, Next.js, JavaFX, Bootstrap, Tailwind CSS, PyTorch} \\
    \textbf{Developer Tools}{: GitHub, VS Code, Postman, Ubuntu, Jupyter Notebook} \\
    \textbf{Backend / DevOps}{: REST APIs, MongoDB, MySQL, JWT Auth, Vercel } \\
    \textbf{Other}{: Agile, Scrum, Unit Testing }
  }}
\end{itemize}



%----------------

%-----------Certificates-----------
\section{Certificates}
\resumeItemListStart
    \resumeItem
    {\textbf{ROS2 For Beginners (Level 1, 2, 3) } $|$ \emph{ https://www.linkedin.com/in/bryananeyro/details/certifications/}}
    
\resumeItemListEnd

 %---------

\end{document}
